Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-21 paper.tex
Justifying use of `print_run`
Refs #39. I will also check it later when examining resulting trees.

As it can be seen in this table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods. On the other hand, \texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by a publisher. In addition, this variable could be interesting to be used to test the prediction model, once it is built. Hence, the publisher could try different values for it and see what the predictor yields, in order to take the best decision.
%Pablo: still waiting the definition of the variables

>>>>

As it can be seen in this table, \texttt{total\_sales} is the output
variable, so it is the objective of the prediction methods. {\tt
  total_sales} are a variable percentage of the {\tt print_run}, and
thus there is obviously some correlation between them, which might
prevent us from using it to predict sales; it is quite obvious that
just increasing the print run, by itself, will not boost
sales. However, several of the other variables include implicitly a
certain size of the print run; for instance, you have to actually
print books to distribute them as novelty and at least one, for every
point of sale, so including the print run makes sense to get more
accurate estimates of the total sales that you are going to obtain out
of the total print run and check its influence on the overall sales
volume. Once this is included in the model and also as part of the
tree nodes, changing the print run might give the publisher an idea of
how many books are going to be actually sold out of that print run,
and taking that into account decide on the actual number of books that
are going to be printed. Just to be clear, printing book does not
actually sell them, but it is obviously necessary to print books
before you sell them, and once you have to do it, the publisher might
make decisions on printing a few more and check, with this model, what
would be the influence in sales if, for instance, you decide to send
more books to every point of sale or distribute more in novelty. We
will come back to this choice later on when examining the resulting
models.
